Human Pose Estimation for Video Game Control

### 2022-05-07 paper/paper.tex
Finished up the related works section

\begin{itemize}
    \item Identify users as sources of input, from a video stream
    \item Segment the user's body to isolate relevant portions of data
    \item Compute location information about the user's body from relevant portions of data.
\end{itemize}

The area of Human Pose Estimation is widely studied. Robust, optimized solutions exist 
that can help us with this step. One popular solution is derived from \cite{8765346} which uses Part Affinity Fields (PAFs) to learn to assosciate body parts with individuals in the image, and 
open-source code for the so called openpose library shows promising results for real-time 
human body segmentation.

@@

\subsection{Gesture Identification/Motion Tracking}
\cite{8765346} and Openpose give us promising ways to identify locations of human body features 
(hands, arms, etc.) in a video stream. However, this is not enough to categorize a user's motion 
as a particular input. To be able to extract feature motion over time as a useful input to our 
car racing video game, we will have to implement motion tracking over a video stream.

A number of guides exist for implementing feature tracking over video. \cite{tracking_1} 
and \cite{tracking_2} demonstrate simple object tracking across video frames, and \cite{tracking_2} 
demonstrates a system shown to be accurate with motion of hands. Implementing a similar system for 
tracking arbitrary features of the human body obtained from human pose estimation should provide 
adequate results.

>>>>

\begin{itemize}
    \item Identify users as sources of input, from a video stream
    \item Segment the user's body to isolate relevant portions of data
    \item Compute the location, in image coordinates, of keypoints on the user's body.
\end{itemize}

The area of Human Pose Estimation is widely studied. There are a wide array of robust, optimized 
solutions for gathering 2D image coordinates of keypoints from images of users.

\subsubsection{Openpose}
One popular solution to realtime human pose estimation, derived from \cite{8765346}, 
uses Part Affinity Fields (PAFs) to learn to assosciate body parts with individuals in the image, 
and open-source code for the so called openpose library shows promising results for real-time 
human body segmentation.

@@

\subsubsection{MoveNet and PoseNet}

PoseNet and its more recent counterpart MoveNet are fully convolutional neural network pose 
estimators built on existing ResNet or MobileNet backbones (citation here). Benchmarks of PoseNet and MoveNet show that it is 
viable to run either estimator in real time on embedded devices with appropriate 
model quantizations (citation here), with PoseNet being slightly faster when compared to MoveNet at identical 
levels of quantization. In comparison's with Openpose, PoseNet/MoveNet are shown to perform 
slightly better on instance segmentation of the person class from the COCO dataset.

\subsection{Gesture Identification/Motion Tracking}
Openpose and MoveNet/PoseNet give us promising ways to identify locations of human body features 
(hands, arms, etc.) in a video stream. However, this is not enough to categorize a user's motion 
as a particular command to a computer system. To be able to extract feature motion over time 
as a useful input to our car racing video game, we will have to implement motion tracking 
over a video stream.\\

A number of guides exist for implementing feature tracking over video. \cite{tracking_1} 
and \cite{tracking_2} demonstrate simple object tracking across video frames, and \cite{tracking_2} 
demonstrates a system shown to be accurate with motion of hands. We drew on \cite{tracking_1} and 
\cite{tracking_2} in developing a tracking algorithm for the identification of a human user ducking 
or jumping from a keypoint cloud.
